**Preprinting Microbiology**

### 2017-04-18 submission/rebuttal.md

**Editor comments:

Overall, the reviewers and I agree that the manuscript is novel, timely, and worth publishing. It is extremely well written, with excellent examples of current and potential applications and outcomes of the use of preprints. With one example, "Arsenic Life" (mentioned kindly), serving as the "poster child" in support of preprints. At the outset, I wondered if he had subjected this paper to the Preprint process (he did) so it includes a "real time" test of the concepts he develops and discusses. The author is to be commended for taking on this study, beyond the call of scientific research papers, and I am sure it will have an impact on thinking about, discussion of, and ultimately the use of preprints in microbial sciences.

Main issues with the manuscript by Reviewer 1 lie primarily with documenting references for many of his assertions. Reviewer 2 comments are very thoughtful, though a bit more philosophical. All points should be considered in a revision, including added citations, and brief additions to the 'history' of preprints. I think an extended discussion of the role of preprints in physics is beyond the scope of this paper. All comments - accepted or not - should be addressed both in a response to reviews with changes to the manuscript noted as well as arguments against changes.**

## Reviewer 1

**1. This is overall an excellent and very useful paper on preprints in one general area (microbiology)

2. I believe the overall analysis is sound and the claims are generally supported by the evidence.

3. There are a few areas of the manuscript that could use modification - mostly just additional detail. I provide line by line comments for any part of the manuscript that I believe could use some modification below.

4. It would be good if all references to web sites include a data when the web site was accessed and in many cases it would be good to include some information from the site as supplemental material. After all, web sites can change and referencing them is tricky. More detail in line by line comments below.

5. The posting of a reproducible version of the analysis in Github is great and I would recommend highlighting this in the text when the analysis is first mentioned.**

**Lines 18 and 19.

"Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues (5)"

I think it would be good to discuss a little bit more the history of preprints and of sharing manuscripts prior to publication. The text here makes it seem like preprint sharing started in the 1960s when I believe this is untrue. The reference cited here appears to focus on organized efforts to share preprints in the 60s (e.g. an attempt by NIH and efforts by the physics community). While important these were not the beginning of preprints and thus the text is a bit inaccurate

In addition, I think it is not quite accurate to say this was a means of "sharing interesting research among colleagues". The efforts in the 60s were attempts to make preprints more broadly available and with less of a bias where some people saw preprints but others did not.

Furthermore, I think there were probably many reasons why people did this including establishing priority and staking out territory (i.e., it was not just about sharing interesting research among colleagues).**

**Line 36

"preprints are typically publicly available in about 24 hours"

Is there data supporting this claim**

**Lines 42-45

"This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations"

Is there a reference for this claim?**

**Lines 48-49

"their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. Proceedings of the National Academy of Sciences). "

Should this read "to a journal as SOME journals"**

**Lines 53-55.

"Compared to the bioRxiv site, the PeerJ Preprint site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints."

This should include a date of accessing the sites and I would recommend perhaps submit screenshots as supplemental material.**

**Lines 55-57

"With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on bioRxiv."

and

Lines 57-58.

"The only direct submission mechanism for manuscripts submitted at PeerJ Preprint is to the PeerJ journal"

A reference / web link would be useful here. Plus a date when these policies were examined would be helpful. I would recommend including the text of the policies as supplemental material if possible.**

**Lines 68-71.

"A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources. A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org)."

It would be good to include the date of access of these sites and if possible some additional information in supplemental material such as text from the site or screen captures to support the text.**

**Lines 72-73

There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications.

Please clarify. Hope from whom?**

**Lines 81-83.

"First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities"

DURC is not just about terrorist activities - it is about any possible misuse of research information.**

**Lines 83-85

"Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research."

I would suggest adding a line here about animal research too and how it is critical that appropriate reviews were done for such research.**

**Lines 89-90

"Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers"

Could you clarify or provide examples of what you mean by policies.**

**Lines 100-101.

"Each take a generally permissive stance towards posting of preprints prior to submission."

Given the following sentences about journal policies changing it would be good to mention how the journal policy was inferred and if possible include references and or web links with dates and such.**

**Line 145-146.

"Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second."

I personally agree with this statement but many in the community do not. This only works if people view preprints as valid publications. There are many examples where peer reviewed papers have been published claiming priority on some novel finding when preprints existed on the topic and where the authors of the peer reviewed paper and sometimes the editors of the journal have stated something akin to "we do not consider preprints valid papers".**

**Lines 160-162.

"Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts."

It would be helpful to reference examples of people expressing such fear if they are available online anywhere.**

**Lines 173-176

"In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications."

References / links would be very useful here.**

**Lines 193-195

"Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus."

I think the wording here and in a few other places in the paper is a bit confusing or awkward. Preprints are published too. So I would suggest using some alternative wording to "published" for papers that have gone through peer review vs. preprints for those that have not.**

**Lines 207-214

Discussion of NY Subway metagenomics.

I think an important part of the story has been left out. On February 17, 2015 Chris Mason wrote a long blog post (at the request of this reviewer) for microBEnet about their paper and about some of the challenges in inferring the presence of anthrax in the subway. See
https://www.microbe.net/2015/02/17/the-long-road-from-data-to-wisdom-and-from-dna-to-pathogen/**

**Lines 265-267

"Although the hosted commenting is only one mechanism for peer review, this result was somewhat disturbing since the preprint model implicitly depends on people's willingness to offer others feedback."

Any information you could provide on the relative balance of commenting in other systems (e.g., Twitter, Facebook, Blogs) would be very helpful here. Or perhaps at least refer to the discussion later in the article**

**Lines 301-303

"Although it is impossible to quantify the quality or impact of research with individual metrics, it is clear that preprints and the publications that result from them are broadly accepted by the microbiology community"

I would love for this to be true. But I am not sure I completely follow the logic of this claim here. Could it not be that the citations for preprints are mostly coming from the authors of those preprints? I know we in my lab cite our preprints quite a bit. Or could it be that a subset of the community cites preprints a lot but others do not?**

## Reviewer #2

**One of the first and most acute causes of culture shock in physicists who have fallen among biologists is the relative role played by preprint servers in the two sciences. The arxiv has been a standard part of physics for years; a place where preliminary results can be displayed, critiqued and refined. In contrast biology preprint servers like biorxiv have only recently begun to attract attention and widespread use. For those who don't yet know about preprints, this perspective is a good introduction.

The MS is very strong on educating the reader about preprints and their advantages for an individual researcher. But less so when it comes to the advantages to the field in general. I think this is important, because the value to the individual and the field are entwined with how preprints are viewed, and the respect in which they are held, and this article is an opportunity to push the dial in the direction of more respect.

Physics and biology are very different enterprises. The position of arxiv in the former is not (only) due to a more open-minded attitude among physicists, but the history of the science and the esteem in which preprints are held. So in a highly competitive field such as Fermi gas microscopy, researchers upload their work as soon as possible and their priority is recognized. Similarly, dense theoretical work can be trialed online in front of a tiny community of peers who can suggest alternatives. These may be extremes/caricatures, but it is true that the important factor is the status of preprints in the community. And while preprints have all the advantages stated in this article, unless their status changes they will remain underused.

In a high status preprint world, as the MS states, publishing on a preprint server does get your paper out and could be seen as 'scooping' competitors. But we are a very long way from that at present. Why cite a preprint that came out well over a year ago, and is accepted but still waiting to see the light of day, when there's an alternative in a glamor journal that came out a few months later? The preprint might get some nice comments on twitter, but nobody is going to see it as having priority.

Also in a high status preprint world, folks would be more likely to comment. At the moment, only a few preprints get many comments, which limits the value of the approach quite a lot. I know the MS says this, but it could say more about it as without this many of the advantages claimed for preprints fall away - so what if you can show your preliminary findings to the world if the world doesn't give you feedback? I suspect it is also true that the numbers of comments are not only down to the inherent interest of the content, but also the profile of the authors. If Nick Loman (for example) puts something on twitter about his preprint, it will get looked at more. Similarly a Very Eminent Scientist* has tried to convince me that the large amount of attention and comments their preprints receive is wholly down to their extraordinary high quality, and has nothing to do with the fact that they are member of the National Academy with a very high profile. Such distortions will never go away, but might be less likely if preprints were consumed with the same interest as 'proper' journals.

So I urge some rewriting to raise these issues -perhaps explicitly recommending that funders mandate that papers should be put up as preprints at the same time they are initially submitted for publication. I have the following specific points I noted as I was reading**

**Line 14 - these other things like blog posts seem interesting, but quite different from preprints. I'd suggest ditching them or making the focus clearer**

**64 repetitions of landscapes fractured etc**

This sentence has been edited to minimize the repetition.

**82 and beyond. Several issues are raised here that are never fully dealt with. The most important is DURC. I think you should say a bit more about how this can be handled responsibly, and the potential for preprints to be subject to minimal review to prevent some of these things.**

**186 Could preprints not attract adversarial comments as well? I am not sure scientists are fully free from the attributes of BTL commentators. What about the possibility of vexatious criticisms? This could be especially true for 'political' topics.**

**249 I wonder if preprints are more common in fields with a high proportion of physics types?**

**286 the public, or other scientists?**

**294 impact factors are 'more traditional' than altmetric, but more 'controversial'? I have to say this made me giggle. I also confess I have no idea how to interpret these scores so this bit was useful to me.**

**301 The comparisons with mBio are really neat, but there is a skew evident in the comparison of the means and median citations. It looks like the majority of preprints get very few citations, but a few get many more. The mBio citations look more normally distributed. Can you say more about this?**

**321 I think this is a bit misleading as review is still needed before publication. Sidestepping is not possible.**

**365 brining? :)**

This has been corrected to "bringing"

### 2017-04-19 submission/Schloss_PrePrints_mBio_2017.Rmd
First pass at responding to reviewers' comments

@@

micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))

@@

***Background.*** Many scientists, including microbiologists, have begun to use preprints and other online venues such as social media, blog posts, and videos as methods to garner attention for their research and to engage the public. A preprint is an interim research product, such as an unpublished manuscript, made publicly available before going through an official peer-review process [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016]. Authors can post their manuscript to a preprint server for others to read, share, and comment. Preprints were initially adopted among physicists and biologists in the 1960s as a method of sharing interesting research amongst colleagues [@Nature1966]. While the biological community's commitment to preprints waned, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. Both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by non-profit organizations. Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to a journal as journals will not consider manuscripts posted as preprints under a CC-BY license (e.g. *Proceedings of the National Academy of Sciences*). The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results; however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option. A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints. With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. The only direct submission mechanism for manuscripts submitted at *PeerJ Preprint* is to the *PeerJ* journal. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also worth noting that numerous other opportunities exist for other forms of interim research products (e.g. blog posts, videos, protocols, etc.) to obtain DOIs that make the work citable. As these possibilities increase, the preprint landscape risks becoming fractured.

One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the preprint landscape. Several examples of these efforts already exist and it likely that these interfaces and their ability to span the landscape will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources. A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org). There is also hope that the National Institutes of Health (NIH) will renew their interest in indexing preprints as separate research products than peer-reviewed publications. As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted. It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider. It is critical that assurances be given that policies are in place to address these issues. First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in terrorist activities. Second, for researchers engaging in research that involves human subjects it is critical that assurances be made that institutional review boards have been consulted and have approved of the research. Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results. Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct. Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have policies for these issues in place that should be easy to implement by preprint servers. It is possible that if preprint usage continues to expand, many of these problems may also grow as has been experienced in the expansion of the traditional publishing industry.

@@

First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal. Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second. Furthermore, a preprint could prevent getting scooped since a preprint would indicate to others in the field that the work had already been done, which would prevent wasted time and effort. The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations. A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016]. Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016]. This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data. As preprints gain broader adoption, the tension between establishing primacy and the completeness of the preprint may test the policies of preprint-friendly journals.

A second area of concern is whether a preprint can be used to support a grant proposal. Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data. Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts. One would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science. This would be greatly facilitated if funding agencies would include preprints as evidence for research progress, but listed separately from peer-reviewed publications to help review panels in their decisions and to help author substantiate evidence they feel they need to provide.

A third concern is what role preprints should have in assessing a scientist's productivity. Clearly use of publication metrics as an indicator of a scientist's productivity and impact is a contentious topic without even discussing the role of preprints. Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee would significantly enhance an application and a reviewer's ability to judge the application. In fact, several funding agencies including the Wellcome Trust and the UK Medical Research Council encouraging fellowship applicants to include preprints in their materials; meanwhile, the NIH is in the process of soliciting input from the scientific community on their role in grant applications. Others are mandating that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].

@@

***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial. In contrast, preprints represent a rapid and potentially collaborative method for disseminating research. Several anecdotes from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of March 2017 the number of Zika virus-related publications was over 2,000. During the recent outbreak, more than 130 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Another interesting use of preprints to disseminate new information about Zika virus has been the posting of a preprint describing the Zika virus outbreak in the US Virgin Islands that will be continually updated as new data and analyses are performed [@Black2017]. Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 100 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on December 31, 2016. I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, *pathogen*, or *protist*. I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.

@@

>>>>

*published* vs. *peer-reviewed*

@@

@@

***Background.*** A preprint is an interim research product, such as a manuscript draft, that is made publicly available before going through an official peer-review process with the goals of soliciting feedback, accelerating dissemination of results, establishing priority, and publicizing negative results [@Vale2015; @DesjardinsProulx2013; @Berg2016; @Bhalla2016; @NIH_NOTICE]. Authors can post their manuscript to a preprint server for others to read, share, and comment. Information Exchange Groups were the first formal attempt to disseminate paper-based preprints among physicists and biologists in the 1960s as a formal mechanism of broadly sharing research [@Nature1966; @Till2001]. While the biological community's commitment to preprints waned by 1967, the physics community adopted what is now the *arXiv* (pronounced "archive") preprint server that was hosted at the Los Alamos National Laboratories from 1991 to 1999 and then at Cornell University [@Ginsparg2011]. For some physicists and mathematicians, posting a preprint to *arXiv* optionally followed by submission to a peer-reviewed journal has become a standard publication pathway. Although *arXiv* has hosted a number of computational biology papers, the server has not drawn widespread attention from biologists. Among proponents of *arXiv*, preprints have aided in the development of research communication by accelerating the release of the science and helping it to achieve a wider audience for critique and reception [@Shuai2012]. Considering the broadening adoption of preprints among microbiologists, I sought to explore the specific uses of and concerns regarding preprints.

***Landscape of preprint servers.*** In 2013, two preprint servers, the *bioRxiv* (pronounced "bio-archive") and *PeerJ Preprints*, were launched as preprint servers for biologists that would parallel *arXiv* [@Callaway2013]. According to information provided on the *bioRxiv* and *PeerJ Preprints* websites both platforms offer similar features: preprint posting is free; each preprint receives a digital object identifier (DOI) that facilitates the ability to cite preprints in other scholarly work; if the preprint is ever published, the preprint is linked to the published version; the submission process for both options is relatively simple allowing authors to upload a PDF version of their preprint and supplemental materials; preprints are typically publicly available in about 24 hours; they have built-in venues for authors to discuss their research with people who leave comments on the manuscript; preprints undergo a basic screening process to remove submissions with offensive or non-scientific content; and the sites provide article-level metrics indicating the number of times an abstract has been accessed or the preprint has been downloaded. There are several important differences between the two options. First, *PeerJ Prints* is a for-profit organization and *bioRxiv* is a non-profit organization sponsored by Cold Spring Harbor Laboratory. This difference can be meaningful to authors since some journals, including the American Society for Microbiology (ASM) Journals, will only accept submissions that have been posted on preprint servers hosted by not-for-profit organizations (http://mbio.asm.org/site/misc/journal-ita_edi.xhtml#02). Second, preprints at *PeerJ Preprints* are posted under the Creative Commons Attribution License (CC-BY) and *bioRxiv* preprints can be posted under one of four CC-BY licenses or with no permission for reuse. This can be relevant for authors hoping to submit their work to *Proceedings of the National Academy of Sciences* as they will not consider manuscripts posted as preprints under a CC-BY license. The NIH encourages authors to post preprints under the CC-BY or public domain licenses [@NIH_NOTICE]. The flexibility of the *bioRxiv* licensing empowers authors to choose the model that best suits them, while ensuring the rapid posting of their research results; however, it is important to provide clear information to authors on the legal and practical tradeoffs of each option. A cosmetic, but still relevant difference between the two is the layout and feel of the two websites. Compared to the *bioRxiv* site, the *PeerJ Preprint* site is more fluid, gives readers the ability to "follow" a preprint, and provides better access to article keywords and the ability to search preprints (Figures S1 and S2). With broader acceptance of preprints by traditional journals, many journals, including all of the ASM journals, have established mechanisms to directly submit manuscripts that are posted as preprints on *bioRxiv*. The only direct submission mechanism for manuscripts submitted at *PeerJ Preprint* is to the *PeerJ* journal. In many ways, preprint servers have taken on the feel of a journal. As adoption of this approach expands, it is likely that the features of these sites will continue to improve. It is also worth noting that numerous other opportunities exist for other forms of interim research products (e.g. blog posts, videos, protocols, etc.) to obtain DOIs that make the work citable. As these possibilities increase, the preprint landscape risks becoming fractured.

One solution to the fracturing of the preprint landscape would be indexing sites that allow a user to easily search for content across the various preprint servers. Several examples of these efforts already exist and it likely that these interfaces and their ability to span the landscape will improve. For example, although Google Scholar includes preprints hosted at *bioRxiv* and *PeerJ Preprints* in their search results, PubMed and Web of Science do not. A relatively new example of what this might look like is PrePubMed (http://www.prepubmed.org/), which seeks to index preprints from numerous sources. A more organized effort is being initiated with funding through ASAPbio to create a "Central Service" that would aggregate preprints in the life sciences (http://asapbio.org/category/central-service). As preprint servers and other content providers begin to look and act like traditional journals by incorporating features and interfaces, it is important to value the strength of the preprint - that of an interim research product, nimble and quickly posted. It is therefore essential to balance the requirements placed on authors for features associated with preprints with the current desirable efficiency of the preprint format.

***Specific challenges for microbiology.*** Although preprints offer an efficient and novel venue for disseminating microbiology research, there are several considerations that the scientific community and those that oversee preprint servers must consider. It is critical that assurances be given that policies are in place to address these issues. First, a significant amount of attention has to be given to the potential dual use research of concern (DURC) since posted results in microbiology research could offer insights to individuals seeking to engage in inappropriate activities. Second, for researchers engaging in research that involves human subjects and other vertebrates it is critical that assurances be made that institutional oversight committees have been consulted and have approved of the research. Third, there is significant concern regarding researchers hiding potential conflicts of interest that could affect a project's experimental design, analysis, and interpretation of results. Finally, recent expansions in scientific publishing have revealed numerous cases of plagiarism or misconduct. Again, while hoping to maintain the efficiency of the preprint format, traditional microbiology journals have screening procedures and oversight committees that address these issues that should be easy to implement by preprint servers. It is possible that if preprint usage continues to expand, many of these problems may also grow as has been experienced in the expansion of the traditional publishing industry.

@@

First, a common concern is that if a researcher posts their work as a preprint, it will be "scooped" by another researcher and the preprint author will lose their ability to claim primacy or their ability to publish the work in a journal. Considering the preprint is a citable work with a DOI, it would, in fact, be the preprint author that scooped the second. Furthermore, a preprint could prevent getting scooped since a preprint would indicate to others in the field that the work had already been done, which would prevent wasted time and effort. The use of preprints uncouples the communication of the discovery from the relevance of the discovery, which will come later based on peer-review, comments from other scientists at meetings or online, and eventually citations. A growing number of scientific societies and journals, including ASM view preprints as citable and as having a legitimate claim to primacy [@Pulverer2016; @Loew2016; @Vale2015; @Vale2016]; however, it remains to be determined whether the journals will stand by these policies. Some scientists worry that with such protection a researcher can make a claim without valid data to support their claims [@Berg2016]. This is possible; however, it is also the responsibility of the scientific community to utilize the peer-review mechanisms that are available to comment on those preprints pointing out methodological problems or to indicate that they are speaking beyond the data. As preprints gain broader adoption, the tension between establishing primacy and the completeness of the preprint may test the policies of preprint-friendly journals.

A second area of concern is whether a preprint can be used to support a grant proposal. Given the length limitations placed on grant proposals by funding agencies, there is a push to cite previous work to indicate a research team's competence in an area or to provide preliminary data. The National Institutes of Health (NIH) recently released a notice clarifying their position on the use of preprints and synthesizing feedback that they received as part of a request for information [@NIH_NOTICE]. In this notice, the NIH indicated that preprints can be cited anywhere that other research is cited including research plans, bibliographies, biosketches, and progress reports. Some fear that the use of preprints will allow scientists to circumvent page limits by posting preliminary manuscripts [@FASEB_letter]. One would hope that both consumers of preprints and grant proposal reviewers would be able to differentiate between someone trying to game the system and someone that is using preprints as a mechanism to improve their science. This would be greatly facilitated by following the NIH recommendation of using preprints as evidence for research progress, but providing an indication that the preprints are not peer-reviewed publications [@NIH_NOTICE]. This would help review panels in rendering their decisions and help author substantiate evidence they feel they need to provide.

A third concern is what role preprints should have in assessing a scientist's productivity. Clearly use of publication metrics as an indicator of a scientist's productivity and impact is a contentious topic without even discussing the role of preprints. Regardless, given the propensity for researchers to list manuscripts as being "in preparation" or "in review" on an application or curriculum vitae, listing them instead as preprints that can be reviewed by a committee would significantly enhance an application and a reviewer's ability to judge the application. In fact, several funding agencies including the NIH, Wellcome Trust, UK Medical Research Council encouraging fellowship applicants to include preprints in their materials [@NIH_NOTICE]. Other funding agencies have mandated that researchers post preprints for all of their work prior to submitting the work to a journal [@Dolgin2016].

@@

***Microbiology anecdotes.*** The peer-review editorial process can be lengthy and adversarial. Because preprints are public and freely available they represent a rapid and potentially collaborative method for disseminating research. Several anecdotes from the microbiology literature are emblematic of benefits of the rapid release cycle that is inherent in the use of preprints.

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of March 2017 the number of Zika virus-related publications was over 2,000. During the recent outbreak, more than 130 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was formally published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Another interesting use of preprints to disseminate new information about Zika virus has been the posting of a preprint describing the Zika virus outbreak in the US Virgin Islands that will be continually updated as new data and analyses are performed [@Black2017]. Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 100 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

***Metrics for microbiology-affiliated preprints.*** To analyze the use of preprints, I downloaded the *bioRxiv* on April 17, 2017. I chose to analyze *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` *bioRxiv* preprints compared to the 2,911 preprints that were available at *PeerJ Preprint* on the same date. The code used to analyze these preprints and the rest of this manuscript are available as a reproducible GitHub repository at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or the Scientific Communication and Education categories. To counter this limitation, I developed a more permissive approach that classified preprints as being microbiology-affiliated if their title or abstract had words containing *yeast*, *fung*, *viral*, *virus*, *archaea*, *bacteri*, *microb*, *microorganism*, *pathogen*, or *protist*. I identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts that I considered microbiology-affiliated. These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r non_micro_category_counts[3]`) categories.

@@

**Supplemental Figure 1. Screen shot of the preprint for this manuscript at bioRxiv.**

**Supplemental Figure 2. Screen shot of a preprint by the author hosted at PeerJ Preprints.**
